The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-05-20 ms.Rmd
cleaning out some bugs in the doc

```{r knitrOpts, echo = FALSE, cache = FALSE, eval = FALSE}
opts_chunk$set(fig.path = 'figs/', message = FALSE, dev = c('pdf', 'png'), cache = TRUE)

@@

@@

This has presented computational science with a very modern version of the reproducibility problem as computational research is largely inaccessible (). If research materials and outputs are shared, they are rarely in a readily modifiable or extensible format despite the great potential for distributing these resources digitally (e.g. Fig Share, Git Hub). The ZOӦN R package aims to address these issues for Species Distribution Modelling by allowing users to encode SDM analyses as workflows comprised of independently executable modules. The module-workflow structure offers a format by which scientists can more easily to create and share components of their analysis, and then access, modify, reuse and combine the components of others (see below and Figure 1).

@@

![The interactive map module overlay the raw data and predicted distribution, allowing users to interactively explore their results.\label{fig:interactive}](./figs/interactive_map.png)

@@

# Load the data into the global environment
data(carw, envir = environment())

@@

```{r merowWorkingCopy, eval = TRUE}

Merow_Silander <- workflow(
    occurrence = Chain(LocalOccurrenceData('occurrenceType = 'presence' ),
                       LocalOccurrenceData(occurrenceType = 'presence/absence', externalValidation = TRUE)),
     covariate = LocalRasterData('CarolinaRasters'),
       process = Chain(Transform(trans = 'square', replace = FALSE), 
                       Background(n = 10000)),
         model = list(LogisticRegression, MaxEnt, MaxLike),
        output = Chain(PerformanceMeasures, PointBiserialCorr, PrintMap)

>>>>

```{r knitrOpts, echo = FALSE, cache = FALSE, eval = FALSE}
# set up knitr options
opts_chunk$set(fig.path = 'figs/',
               message = FALSE,
               dev = c('pdf', 'png'),
               cache = TRUE)

@@

```{r raster_dir, echo = FALSE, cache = FALSE, eval = TRUE}
# set a place for the rasters to be downloaded to (to stop them being grabbed
# again each time)
raster_dir <- './raster_data'
if (!dir.exists(raster_dir)) dir.create(raster_dir)
options("rasterDataDir" = raster_dir)
```

@@

This has presented computational science with a very modern version of the reproducibility problem as computational research is largely inaccessible (). If research materials and outputs are shared, they are rarely in a readily modifiable or extensible format despite the great potential for distributing these resources digitally (e.g. Fig Share, Git Hub). The ZOON R package aims to address these issues for Species Distribution Modelling by allowing users to encode SDM analyses as workflows comprised of independently executable modules. The module-workflow structure offers a format by which scientists can more easily to create and share components of their analysis, and then access, modify, reuse and combine the components of others (see below and Figure 1).

@@

![The interactive map module overlays the raw occurrence data and predicted distribution over a global map, allowing users to interactively explore their results.\label{fig:interactive}](./figs/interactive_map.png)

@@

# Load the data into the global environment
data(carw, envir = environment(), package = 'maxlike')

@@

```{r merowWorkingCopy, eval = FALSE}

Merow_Silander <- workflow(
    occurrence = Chain(LocalOccurrenceData(occurrenceType = 'presence'),
                       LocalOccurrenceData(occurrenceType = 'presence/absence',
                                           externalValidation = TRUE)),
     covariate = LocalRaster('CarolinaRasters'),
       process = Chain(Transform(trans = 'square',
                                 replace = FALSE), 
                       Background(n = 10000)),
         model = list(LogisticRegression, MaxEnt, MaxLike),
        output = Chain(PerformanceMeasures, PointBiserialCorr, PrintMap))
